%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {Kitabisa} % Organisation
    {Jakarta, Indonesia} % Location
    {May 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working with campaigner squad to develop features related to the campaign.}
         \item {Develop an internal product library called KBPL and already published some components like image, bottomsheet , chips, and menu navigation.}
         \item { Develop revamp campaign detail especially fund detail. }
        \item {\textbf{Technical Skills:} Typescript , Javascript , ReactJs , NextJS , Git , TailwindCss}
        \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation skills.}
      \end{cvitems}
    }
    
    %---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {PUTI - Telkom University} % Organisation
    {Bandung, Indonesia} % Location
    {Mar 2021 - Apr 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working on an internal project for the international office app for managing student permits its called permit service.}
        \item {Contribute to work on an application project to manage the certification of Telkom University employees and students called DigiTrain.}
        \item {Develop dashboard portal data for academic Telkom university.}
        \item {\textbf{Technical Skills:} Typescript , Javascript , ReactJs , AngularJS , Git , SCSS , Bootstrap.}
        \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation skills.}
      \end{cvitems}
    }
    
        
    %---------------------------------------------------------
  \cventry
    {Internship} % Job title
    {Vallet} % Organisation
    {Bandung, Indonesia} % Location
    {Jan 2020 - Apr 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Manage assets images at vallet app.}
        \item {Take image assets for publish on vallet app.}
        \item {Make assets like poster , banner etc.}
        \item {\textbf{Technical Skills:} Photoshop . Vallet app ( design tools ) , Photography .}
        \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication.}
      \end{cvitems}
    }
    
        %---------------------------------------------------------
  \cventry
    {Internship} % Job title
    {Inovasi Semesta Ilmu (INOSI)} % Organisation
    {Bandung, Indonesia} % Location
    {Jan 2018 - Feb 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop augmented reality virtual tour Bandung.}
        \item {\textbf{Technical Skills:} C\#  , Unity 3D.}
        \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
